---
title: "R Notebook"
output: html_notebook
---

Week 20 - Broadband data. First load the data. 

```{r data}
library(tidytuesdayR)
library(tidyverse)

tuesdaydata <- tidytuesdayR::tt_load('2021-05-11')

broadband <- tuesdaydata$broadband

broadband_zip <- tuesdaydata$broadband_zip

```

Explore and clean data

```{r Explore}

library(DataExplorer)

#Clean Broadband data

broadband <- broadband %>% janitor::clean_names()

#glimpse(broadband)

fact_cols <- c('st')

dbl_cols <- c('broadband_availability_per_fcc', 'broadband_usage')

char_Cols <- c('county_id')

broadband <- broadband %>% 
  mutate(across(.cols = all_of(fact_cols), .fns = as_factor),
         across(.cols = all_of(dbl_cols), .fns = as.double),
         across(.cols = all_of(char_Cols), .fns = as.character))

#introduce(broadband)

broadband <- broadband %>% drop_na(broadband_usage)


#Clean broadband_zip data

#glimpse(broadband_zip)

broadband_zip <- broadband_zip %>% janitor::clean_names()

char_Cols <- c('county_id', 'postal_code')
fact_cols <- c('st')

broadband_zip <- broadband_zip %>% 
  mutate(across(.cols = all_of(char_Cols), .fns = as.character),
         across(.cols = all_of(fact_cols), .fns = as_factor))

```
Build following type of graphs.

Broadband dataset- broadband usage

1. Box Plot by state
2. Ridge Plot by state
3. Timehorizon type chart by state
3. Chloropeth map by county

How do I credit tidytuesday


Broadband Zip dataset- broadband usage

1. Box Plot by state
2. Ridge Plot by state
3. Timehorizon type chart by state
3. Chloropeth map by zip code



Let us build a box plot by state.

```{r Box_Plot}

bu_county <- broadband %>% ggplot(aes(broadband_usage, reorder(st, broadband_usage, median))) + geom_boxplot() +
  labs(title = "Broadband usage by state", 
       y = "State",
       x = "Broadband Usage",
       subtitle = "Based on County Data",
       caption = "#TidyTuesday \n Week 20 Broadband Usage Data")

bu_zip <- broadband_zip %>% ggplot(aes(broadband_usage, reorder(st, broadband_usage, median))) + geom_boxplot() +
  labs(title = "Broadband usage by state", 
       y = "State",
       x = "Broadband Usage",
       subtitle = "Based on Zip Data",
       caption = "#TidyTuesday \n Week 20 Broadband Usage Data")

library(patchwork)

broad_band_box <- bu_county + bu_zip

broad_band_box

ggsave(here::here("Week 20 - Broadband", "Output", "BroadBandUsageBoxPlot.png"), width = 10.5, height = 8, units = "in")

```
Ridge Plot

```{r Ridge Plot}

library(ggridges)

  bb_ridge_county <- broadband %>% ggplot(aes(broadband_usage, reorder(st, broadband_usage, median))) + geom_density_ridges() +
  xlim(c(0,1)) +
  labs(title = "Broadband usage by state", 
       y = "State",
       x = "Broadband Usage",
       subtitle = "Based on County Data",
       caption = "#TidyTuesday \n Week 20 Broadband Usage Data") 

bb_ridge_zip <- broadband_zip %>% ggplot(aes(broadband_usage, reorder(st, broadband_usage, median))) + geom_density_ridges() +
  xlim(c(0,1)) +
  labs(title = "Broadband usage by state", 
       y = "State",
       x = "Broadband Usage",
       subtitle = "Based on Zip Data",
       caption = "#TidyTuesday \n Week 20 Broadband Usage Data") 

bb_ridge_county + bb_ridge_zip

ggsave(here::here("Week 20 - Broadband", "Output", "BroadBandUsageRidgePlot.png"), width = 10.5, height = 8, units = "in")

```


Choropleth map

I have used the usmap library.

**Important to create county_ids by name fips or state codes by name state if you want to plot by state or counties**

Other important library is **maps**. Some useful documentation can be found over [here.](https://www.rdocumentation.org/packages/maps/versions/3.3.0/topics/map)


Here is a [comprehensive documentation](https://www.r-graph-gallery.com/choropleth-map.html) to create choropleth maps.


[Geocomputation book](https://geocompr.robinlovelace.net/intro.html)

```{r Map}

library(usmap)

broadband <- broadband %>% 
  mutate(fips = if_else(str_length(county_id) == 4, str_c("0", county_id), county_id))

usage <- plot_usmap(data = broadband, values = "broadband_usage", color = "Black") + 
  scale_fill_continuous(name = NULL, low = "white", high = "red") +
  theme(legend.position = "right") +
  labs(title = "Broadband Usage in US Counties",
       caption = "#TidyTuesday \n Week 20 Broadband Usage Data")

ggsave(here::here("Week 20 - Broadband", "Output", "Broadband_Usage.png"), plot = usage, width = 10.5, height = 8, units = "in")


availability <- plot_usmap(data = broadband, values = "broadband_availability_per_fcc", color = "Black") + 
  scale_fill_continuous(low = "white", high = "red") +
  #guides(fill = FALSE) +
  theme(legend.position = "none") +
  labs(title = "Broadband Availability in US Counties")

library(patchwork)

availability + usage + plot_layout(guides = 'collect') + theme(legend.position = "right")

ggsave(here::here("Week 20 - Broadband", "Output", "Choropleth.png"), width = 10.5, height = 8, units = "in")

```

I have trouble putting legend at the bottom.



Leaflet

```{r leaflet map}

library(leaflet)

m <- leaflet() %>% 
  addTiles() %>%  
  addMarkers(lng = 106, lat = 12)

m

```



Time Horizon style map to show ridge plot.

