---
title: "R Notebook"
output: html_notebook
---

Week 20 - Broadband data. First load the data. 

```{r data}
library(tidytuesdayR)
library(tidyverse)

tuesdaydata <- tidytuesdayR::tt_load('2021-05-11')

broadband <- tuesdaydata$broadband

broadband_zip <- tuesdaydata$broadband_zip

```

Explore data

```{r Explore}

library(DataExplorer)

broadband <- broadband %>% janitor::clean_names()

glimpse(broadband)

fact_cols <- c('st')

dbl_cols <- c('broadband_availability_per_fcc', 'broadband_usage')

char_Cols <- c('county_id')

broadband <- broadband %>% 
  mutate(across(.cols = fact_cols, .fns = as_factor),
         across(.cols = dbl_cols, .fns = as.double),
         across(.cols = char_Cols, .fns = as.character))

introduce(broadband)

df <- (is.na(broadband))

df1 <- df %>% rowsum()

create_report(broadband_zip)

```




Let us build a box plot by state.

```{r}



```


When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
